---
title: "ama.ORG"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction
Transforming ORGs (Generalized Odds Ratios) and 95%CI to log ORG (yi) and standard errors (sei). 
These values can be used with the metafor package to plot data


```{r}
library(readr)
library(metafor)
```

## Processing individual ORG files
Meta-analysis of various miRNA polymorphisms has been performed using generalized odds ratio (i.e. ORG). Fixed-effects (FE) and random-effects (RE) ORG meta-analysis for different groups and subgroups have been performed using the provided software for ORG. Each file in the datasets/ORG_raw folder represents the FE & RE models for a single miRNA/subgroup. here, the files are processed and results are concatenated for further analysis and plotting.  
FE & RE data lie between 'Study' and '***META-ANALYSIS***'

```{bash}
cat $PWD/datasets/ORG_raw/146a.African.txt
```

The following chunk process all ORG raw files within `/datasets/ORG_raw/` folder, removes unnecessary parts and concatenate all files together in a single file and also add the name of each file (i.e. the analysis) as a column to keep track of different analysis performed.

```{bash}
[[ ! -d $PWD/datasets/ORG_cleaned  ]] && mkdir $PWD/datasets/ORG_cleaned && cp $PWD/datasets/ORG_raw/*.txt $PWD/datasets/ORG_cleaned

for f in $PWD/datasets/ORG_cleaned/*.txt; do
    sed -n -f '/Study/,/META-ANALYSIS/p' $f
    sed -f '1d' $f             # remove the first line (i.e. header)
    sed -f 's/ \+ /\t/g' "$f"  # convert trailing spaces to a tab, but leave individual spaces intact
    cut -f 2-5 $f >"tmpfile" && mv tmpfile "$f" # remove the first (1) and the last (6) empty column (i.e. tab)
    head -n -2 $f > 'tmpfile' && mv tmpfile "$f"       # remove the last 2 lines
done

## add base filename to the end of each file & concatenate them together
### (split is an awk function)
awk 'BEGIN {FS = "\t"; OFS="\t"} {idx = split(FILENAME, parts, "/"); print $0, parts[idx]}' $PWD/datasets/ORG_cleaned/*.txt > $PWD/datasets/ORG_all.txt
```

## Computing yi & sei from ORGs

```{r}
ORG_all <- read_delim("./datasets/ORG_all.txt", 
                      "\t", escape_double = FALSE, col_names = FALSE, 
                      col_types = cols(X1 = col_skip()), trim_ws = TRUE)

colnames(ORG_all) <- c("ORG", "ci.lb", 'ci.ub', "name")

ORG_all <- within(ORG_all, {
            yi <- log(ORG)
            sei <- (log(ci.ub) - log(ci.lb))/(2*1.96)
})

head(ORG_all)
```

## rma.ORG function
takes a dataframe (df) containing the yi and sei and names of groups (miR)
and returns a list of rma object.

```{r}
rma.ORG <- function(df, miR){
  require(metafor)
  df[[miR]] <- factor(df[[miR]])
  groups <- levels(df[[miR]])
  rma.ORG <- list()
  for (i in 1:length(groups)) {
    dataF <- df[df[[miR]] == groups[i],]
    rma.element <- rma(yi = dataF$yi , sei = dataF$sei, slab = 1:nrow(dataF), method = "DL", data = dataF, test = "z", measure = "OR")
    rma.ORG[[i]] <- rma.element
    names(rma.ORG)[i] <- groups[i]
  }
 return(rma.ORG) 
}

ORGs <- rma.ORG(ORG_all, "name")
```

## perorming influence analysis on ORGs
This chunk performs influence analysis for `rma.ORG` objects stored in `ORGs` and produces appropriate influence plots.
```{r}
for (i in 1:length(ORGs)){
  object <- influence(ORGs[[i]])
  assign(paste0(names(ORGs)[i],"-inf"), object)
  
  tiff(paste0(names(ORGs)[i], "-inf.tiff"), width = dev.size()[1], height =  dev.size()[2], units = 'in', res = 400)
  cairo_pdf(filename = paste0(names(ORGs)[i], "-inf.tiff"), onefile = TRUE, width=5.4,height=7.5, family = "sans", fallback_resolution = 1000)
  plot.infl.rma.uni(influence(ORGs[[i]]))
  dev.off()
}
```






