---
title: "ama.ORG"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction
Transforming ORGs (Generalized Odds Ratios) and 95%CI to log ORG (yi) and standard errors (sei). 
These values can be used with the metafor package to plot data


```{r}
library(readr)
library(metafor)
```

## Processing individual ORG files
Meta-analysis of various miRNA polymorphisms has been performed using generalized odds ratio (i.e. ORG). Fixed-effects (FE) and random-effects (RE) ORG meta-analysis for different groups and subgroups have been performed using the provided software for ORG. Each file in the datasets/ORG_raw folder represents the FE & RE models for a single miRNA/subgroup. here, the files are processed and results are concatenated for further analysis and plotting.  
FE & RE data lie between 'Study' and '***META-ANALYSIS***'

```{bash}
cat $PWD/datasets/ORG_raw/146a.African.txt
```

The following chunk process all ORG raw files within `/datasets/ORG_raw/` folder
```{bash}
for i in $PWD/datasets/ORG_raw/*.txt; do
sed -n -i '/Study/,/META-ANALYSIS/p' $i
sed -i '1d' $i                         # remove the first line
sed -i 's/ \+ /\t/g' "$i"  # convert trailing spaces to a tab, but leave individual spaces untact
cut -f 2-5 $i >"tmpfile" && mv tmpfile "$i" # remove the first (1) and the last (6) empty colum (tab)
head -n -2 $i >"./t/M-${i}"                 # remove the last 2 lines
done

## add base filename to the end of each file
### split is an awk function
awk 'BEGIN {FS = "\t"; OFS="\t"} {idx = split(FILENAME, parts, "/"); print $0, parts[idx]}' /mnt/e/test/*.txt
```


## Computing yi & sei from ORGs

```{r}
ORG_all <- read_delim("./datasets/ORG.all.txt", 
                      "\t", escape_double = FALSE, col_names = FALSE, 
                      col_types = cols(X1 = col_skip()), trim_ws = TRUE)

colnames(ORG_all) <- c("ORG", "ci.lb", 'ci.ub', "name")

ORG_all <- within(ORG_all, {
            yi <- log(ORG)
            sei <- (log(ci.ub) - log(ci.lb))/(2*1.96)
})
```



